---
title: "Homework 6"
author: "Mia Murphy"
date: "3/28/2021"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---


### 1

```{r}
#Assign to the variable n_dims a single random integer between 3 and 10.
n_dims<- as.integer(runif(1, 3, 10))
print(n_dims)
```
```{r}
#Create a vector of consecutive integers from 1 to n_dims^2.
vec_a<- c(1:(n_dims)^2)
print(vec_a)
```
```{r}
#Use the sample function to randomly reshuffle these values.
vec_b<- sample(x=vec_a)
print(vec_b)
```
```{r}
#Create a square matrix with these elements
matrix_a<- matrix(data=vec_b,
                  ncol=n_dims, 
                  nrow=n_dims)

#Print out the matrix.
print(matrix_a)
```
```{r}
#Find a function in r to transpose the matrix.
trans_matrix_a<- t(matrix_a)
print(trans_matrix_a)
```
```{r}
#Print it out again and note how it has changed.
print(trans_matrix_a)
```
Diagonals inverse. 20 swaps with 24, 32 with 14, etc.

(Comparing the first and last print, not middle and last print).

```{r}
#Calculate the sum and the mean of the elements in the first row and the last row.
sum_a<- sum(trans_matrix_a[1])
print(sum_a)
mean_a<- mean(trans_matrix_a[1])
print(mean_a)
```
```{r}
sum_b<- sum(trans_matrix_a[n_dims])
print(sum_b)
mean_b<- mean(trans_matrix_a[n_dims])
print(mean_b)
```
```{r}
#Read about the eigen() function and use it on your matrix
eigen_time<- eigen(trans_matrix_a, symmetric=TRUE)
print(eigen_time)
```

Look carefully at the elements of $values and $vectors. What kind of numbers are these?

Eigan values are numbers of any value and eigan vectors are bound between -1 and 1.


```{r}
#Dig in with the typeof() function to figure out their type.
print(typeof(eigen_time))
```

If have set your code up properly, you should be able to re-run it and create a matrix of different size because n_dims will change.

### 2

```{r}
#my_matrix, which is a 4 x 4 matrix filled with random uniform values
 
#my_logical which is a 100-element vector of TRUE or FALSE values. Do this efficiently by setting up a vector of random values and then applying an inequality to it.

#my_letters, which is a 26-element vector of all the lower-case letters in random order.

my_list <- list(my_matrix = matrix(runif(16), nrow=4),
                my_logical = .5 < runif(100),
                my_letters = sample(letters))

print(my_list)
```
```{r}
#Create a new list, which has the element[2,2] from the matrix, the second element of the logical vector, and the second element of the letters vector.

my_new_list <- list(my_list$my_matrix[2,2], 
                 my_list$my_logical[2],
                 my_list$my_letters[2])
print(my_new_list)
```
```{r}
#Use the typeof() function to confirm the underlying data types of each component in this list

type1 <- typeof(my_new_list[[1]])
type2 <- typeof(my_new_list[[2]])
type3 <- typeof(my_new_list[[3]])
print(type1)
print(type2)
print(type3)
```
```{r}
#Combine the underlying elements from the new list into a single atomic vector with the c() function.
my_vector <- c(my_new_list[[1]],
               my_new_list[[2]],
               my_new_list[[3]]) 
print(my_vector)
```
```{r}
#What is the data type of this vector?
print(typeof(my_vector))
```

### 3

```{r}
#Create a data frame with two variables (= columns) and 26 cases (= rows).
#Call the first variable my_unis and fill it with 26 random uniform values from 0 to 10
#Call the second variable my_letters and fill it with 26 capital letters in random order.

my_unis <- runif(26, 0, 10)
my_letters2 <- sample(letters[1:26])

dframe<- data.frame(my_unis, my_letters2)
print(dframe)
```
```{r}
#For the first variable, use a single line of code in R to select 4 random rows and replace the numerical values in those rows with NA.
dframe[sample(nrow(dframe), 4), 'my_unis'] <- NA
print(dframe)

```
```{r}
#For the first variable, write a single line of R code to identify which rows have the missing values.
missing <- dframe[is.na(dframe$my_unis),]
print(missing)
```
```{r}
#For the second variable, sort it in alphabetical order
dframe$my_letters2 <- sort(dframe$my_letters2)
print(dframe)
```
```{r}
#Calculate the column mean for the first variable.
mean(dframe$my_unis, na.rm=TRUE)
```



